---
title: "R With Git and Github"
author: "Aris Paschalidis"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  beamer_presentation:
    theme: "CambridgeUS"
    colortheme: "beaver"
    slide_level: 2
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  ollapse = TRUE,
  comment = "#>")
```

# Setup

## Install Git

Git allows us to track changes to our documents (i.e. Git is version control).

-  Check if git is already installed: `which git`
```{bash, echo = F}
which git 
```

- Install git for Windows: <https://gitforwindows.org/>
- Install git for Mac: `brew install git`
- Install git for Linux:
  + Ubuntu or Debian: `sudo apt-get install git`
  + Fedora or RedHat: `sudo yum install git`
  
## Configure Git

- Introduce yourself to git
```{r, eval = F}
usethis::use_git_config(user.name = "first last",
                        user.email = "github email")
```

- Ensure set-up was successful
```{bash}
git config --global --list 
```

## Managing Git(Hub) Credentials[^ref]

- Adopt HTTPS
- [Secure your account with 2FA](https://docs.github.com/en/github/authenticating-to-github/securing-your-account-with-two-factor-authentication-2fa)
- Create a PAT: `usethis::create_github_token()`
- Store PAT into the Git credential store: `gitcreds::gitcreds_set()`

[^ref]: Following the [usethis guide](https://usethis.r-lib.org/articles/articles/git-credentials.html)

